Global well-being and mental health in the internet age

### 2023-05-30 ms.Rmd
Clarify meta-regression weighting

keywords: well-being, mental health, internet technology, technology effects
wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
bibliography: "references.bib"
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
# header-includes:
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

@@

gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    n = n(),
    se = sd(val, na.rm = TRUE) / sqrt(n),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()

# Note that if there is no response variance, SE will be zero, and if there is only 1 response, SE will be NA. Here we fix those by assigning them the maximum SE (0.5)
gwp <- gwp %>% 
  mutate(
    se = if_else(is.na(se) | se == 0, 0.5, se)
  )

@@

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))

@@

# Selfharm models don't converge with SEs
dat <- dat %>% 
  mutate(se = if_else(outcome == "Selfharm", 0, se))

@@

Before modelling the data, we aggregated the individual-level well-being values to means and standard errors for each country-year-age-sex combination, in order to facilitate the Hamiltonian Monte Carlo computations on large data, and to harmonise the analyses and inferences between Studies 1 and 2. Importantly, we note that because we modelled unweighted demographic- and country-level data, our unit of analyses are demographic groups within countries, with no adjustment to e.g. countries' population sizes.

@@

\begin{align*} 
y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{se}^2_i}), \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{X}^{\text{CW}}_i + \\
&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{X}^{\text{CW}}_i + \\
&\quad\ \alpha_6 \text{X}^{\text{CB}}_i,
\\
\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}), \\
\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}), \\
\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country}),
\end{align*}

where $i$ indexes rows in the data and $\text{se}_i$ are the known standard errors. $\text{X}^{\text{CW}}_i$ and $\text{X}^{\text{CB}}_i$ are the within- and between-country centred internet technology adoption predictor (per capita internet users or mobile broadband subscriptions, in separate models), respectively. We used default noninformative priors on all parameters except the following population-level coefficients, that were modelled as

\begin{align*}
\alpha_{1,3-6} &\sim \text{Normal}(0, 1), \\
\alpha_{2} &\sim \text{Normal}(0, 3), \\
\sigma_{\gamma_4} &\sim \text{Normal}^+(0, 0.5).
\end{align*}

We used these priors to help model convergence, and on the assumption that differences in well-being between males and females are likely greater than differences associated with years, one-percent increases in technology adoption predictors, or the interaction terms.

@@

We conducted all data analyses with R [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan's Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021]. We ran 4 HMC chains with 3,000 iterations and first 1,500 as warmup for 6,000 total iterations. We ensured that all population-level parameters' had converged using numeric diagnostics (all Rhats were within 0.01 of 1) and visual inspection of parameters' scatterplot matrices.

>>>>

keywords: well-being, mental health, internet technology, technology effects
wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
bibliography: "references.bib"
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

@@

# Pivot outcomes to long format
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  )

# Aggregate outcomes
gwp <- gwp %>% 
  summarise(
    n = n(),
    sd = sd(val, na.rm = TRUE),
    val = mean(val, na.rm = TRUE),
    .by = c(country, year, sex, age, outcome)
  )

# Assign N of 1 cells a standard deviation of zero
gwp <- gwp %>% 
  mutate(sd = if_else(is.na(sd), 0, sd))

@@

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(sd = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))

@@

@@

Before modelling the data, we aggregated the individual-level well-being values to means, standard deviations, and counts for each country-year-age-sex combination, in order to facilitate the Hamiltonian Monte Carlo computations on large data, and to harmonise the analyses and inferences between Studies 1 and 2. Importantly, we note that because we modelled unweighted demographic- and country-level data, our unit of analyses are demographic groups within countries, with no adjustment to e.g. countries' population sizes.

@@

\begin{align*} 
y_i &\sim \text{Normal}(\mu_i, \sqrt{\sigma^{2} + \text{sd}^2_i}), \\
\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} + \gamma_{0\text{age}[i]} + \delta_{0\text{age:country}[i]} + \\
&\quad\ (\alpha_{1} + \beta_{1\text{country}[i]} + \gamma_{1\text{age}[i]} + \delta_{1\text{age:country}[i]})\text{Time}_i + \\
&\quad\ (\alpha_{2} + \beta_{2\text{country}[i]} + \gamma_{2\text{age}[i]} + \delta_{2\text{age:country}[i]})\text{Sex}_i + \\
&\quad\ (\alpha_{3} + \beta_{3\text{country}[i]} + \gamma_{3\text{age}[i]} + \delta_{3\text{age:country}[i]})\text{Sex}_i \times \text{Time}_i + \\
&\quad\ (\alpha_{4} + \beta_{4\text{country}[i]} + \gamma_{4\text{age}[i]} + \delta_{4\text{age:country}[i]})\text{X}^{\text{CW}}_i + \\
&\quad\ (\alpha_{5} + \beta_{5\text{country}[i]} + \gamma_{5\text{age}[i]} + \delta_{5\text{age:country}[i]})\text{Sex}_i \times \text{X}^{\text{CW}}_i + \\
&\quad\ \alpha_6 \text{X}^{\text{CB}}_i,
\\
\pmb{\beta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{country}), \\
\pmb{\gamma} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age}), \\
\pmb{\delta} &\sim \text{MVN}(\pmb{0}, \Sigma^\text{age:country}),
\end{align*}

where $i$ indexes rows in the data and $\text{sd}_i$ are the known standard deviations. $\text{X}^{\text{CW}}_i$ and $\text{X}^{\text{CB}}_i$ are the within- and between-country centred internet technology adoption predictor (per capita internet users or mobile broadband subscriptions, in separate models), respectively. In addition to the standard deviations, we weighted each observation by the number of respondents in that cell, to adjust for varying sample sizes across cells. We used default noninformative priors on all parameters.

@@

We conducted all data analyses with R [@rcoreteamLanguageEnvironmentStatistical2021] and estimated the models using Stan's Hamiltonian Monte Carlo sampling via the brms R package [@burknerBrmsPackageBayesian2017; @standevelopmentteamStanModelingLanguage2021]. We ran 4 HMC chains with 4,000 iterations and first 2,000 as warmup for 8,000 total iterations. We ensured that all population-level parameters' had converged using numeric diagnostics (all Rhats were within 0.01 of 1) and visual inspection of parameters' scatterplot matrices.
